Cluster Analysis: Identifying Parkinson's Disease Subtypes

### 2015-07-15 writeup/parkinsons.tex
draw the correct bcl heatmap
fix name typo
add feature ranking, start difference tests

\subsection{Dataset Description}
951 subjects, 145 metrics, collected 15-4-2012 from Pablo Martinez \'in. Only
19 features used for clustering and/or interpretation.  50 subjects with
missing values of the features to be used in clustering (brought down to 901).
Imputation may be a good idea later on.

@@

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{biclust-16.pdf}
  \caption{Biclustering $N = 16$}
  \label{fig:biclust-16}
\end{figure}

>>>>

\subsection{Dataset Description}
951 subjects, 145 metrics, collected 15-4-2012 from Pablo Martinez Mart\'in. Only
19 features used for clustering and/or interpretation.  50 subjects with
missing values of the features to be used in clustering (brought down to 901).
Imputation may be a good idea later on.

@@

\subsubsection{Statistical Significance Tests, $k = 4$}
Using one-way ANOVA for multiple means, we reject the null
hypothesis that the means are the same with $p < 0.05$ for every variable
\emph{except} \texttt{pdonset}.

\subsubsection{Ranked Features}

\begin{table}[h]
  \centering
  \caption{Features ranked by information gain}
  \label{tab:info_gain}
  \begin{tabular}{l|l}
    variable & information gain \\
    \hline
    axial      & 0.20640691 \\
    cisitot      & 0.20008571 \\
    pigd      & 0.18193982 \\
    nms\_d2      & 0.13178572 \\
    nms\_d9      & 0.12116024 \\
    bradykin      & 0.11966097 \\
    nms\_d3      & 0.09421859 \\
    rigidity      & 0.09260628 \\
    nms\_d5      & 0.07579997 \\
    nms\_d4      & 0.07438784 \\
    nms\_d6      & 0.06620599 \\
    nms\_d7      & 0.05574956 \\
    nms\_d1      & 0.05509838 \\
    tremor      & 0.04140473 \\
    nms\_d8      & 0.03786173 \\
    durat\_pd      & 0.02794420 \\
    age      & 0.00000000 \\
    sex      & 0.00000000 \\
    pdonset      & 0.00000000 \\
  \end{tabular}
\end{table}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{biclust-heatmaps-16.pdf}
  \caption{Biclustering heatmaps $N = 16$}
  \label{fig:biclust-heatmaps-16}
\end{figure}
